Advances in Artificial Intelligence for Data Visualization: Automate Reading of Diagnostic Plots with Compute Vision Models

### 2023-04-11 Milestone_2/report/report.Rmd
finish the code chunk

>>>>

```{r lineup-example, fig.pos="t!", fig.height = 7, fig.width = 7, fig.cap = "Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot $2^2 + 2$, exhibiting non-linearity) is embedded among 19 null plots, where the residuals are simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot $2^2 + 2$."}
vi_lineup <- get_vi_lineup()
vi_lineup$poly_300$data %>%
  VI_MODEL$plot_lineup(theme = theme_light(), remove_axis = TRUE, remove_grid_line = TRUE)
```
